### 2021-10-02 docs/paper/sections/3_framework.tex
paper: minor phrasing and typesetting improvements
Complements c8b4220099ad8ca7bed862217d56dbd39dc2f602

\begin{enumerate}[label=Q\arabic*]
	\item Which dependencies are using the target package, and what problems do they attempt to solve with it?
	\item By how many dependencies is a particular package member being used?
	\item In which contexts and constellations is a particular package member being used?
\end{enumerate}

@@

In essence, our proposed approach to collect the required data while fulfilling these requirements consists of three steps:
\begin{enumerate*}
	\item collect downstream dependency repositories,
	\item mine package usage samples from them,
	and \item aggregate and present these usage data to the user.
\end{enumerate*}
In the following sections, we will describe each step.

>>>>

\begin{enumerate}[label=Q\arabic*]
	\item \label[question]{q1} Which dependencies are using the target package, and what problems do they attempt to solve with it?
	\item \label[question]{q2} By how many dependencies is a particular package member being used?
	\item \label[question]{q3} In which contexts and constellations is a particular package member being used?
\end{enumerate}

@@

In essence, our proposed approach to collect the required data while fulfilling these requirements consists of three steps:
\begin{enumerate*}[label=(\roman*)]
	\item collect downstream dependency repositories,
	\item mine package usage samples from them,
	and \item aggregate and present these usage data to the user.
\end{enumerate*}
In the following sections, we will describe each step.
